---
title: "Setting up schedule monitor"
format: html
---

Begin by attaching `Bucephala` to your local environment via the `library()` call. 

```{r}
library(Bucephala)
```

If this is your first time getting setup, go ahead and create your associated storage folders. 

```{r}
#| eval: FALSE
FolderSetup()
```

# Set up Login Credentials

```{r}
#| eval: FALSE
UsernameSet()
# UsernameSet(KeyringIgnore=TRUE)
```

```{r}
#| eval: FALSE
PasswordSet()
# PasswordSet(KeyringIgnore=TRUE)
```


# Start Session

Once this is done, proceed to set up a headless-browser session via chromote (make sure to have your phone handy for the 2FA)

```{r}
#| eval: FALSE
Active <- BrowserRun()
Active$view()
```

At this point you should be able to scrape the data. 

# Scraping the Data

This is where the main customization between sites occurs. Thus being kept intentionally external, with the data.frame then being passed to `Bucephala` from where it can operate. 

```{r}
Canto <- "282295#" #1
LSRII <- "282294#" #2
Aria <- "282292#" #3
Aurora3 <- "349299#" #4
Aurora4 <- "456489#" #5
Aurora5 <- "512453#" #6
AuroraCS <- "512475#" #7
MACSQuant10 <- "454785#" #8
Amnis <- "305467#" #9

TheInstrument = c("Canto", "LSRII", "Aria", "Aurora3", "Aurora4", "Aurora5", "AuroraCS", "MACSQuant10", "Amnis")

Code <- c(Canto, LSRII, Aria, Aurora3, Aurora4, Aurora5, AuroraCS, MACSQuant10, Amnis)

Data <- data.frame(
  TheInstrument = c("Canto", "LSRII", "Aria", "Aurora3", "Aurora4", "Aurora5", "AuroraCS", "MACSQuant10", "Amnis"),
  Code = Code
)
```

With the data.frame ready, we can pass it to `BookingRetrieval`, which will parse each instruments page and return a .csv file of the bookings to the data folder.

```{r}
#| eval: FALSE
TheData <- BookingRetrieval(data=Data, chromote_session = Active)
```

# Plotting the Data

Bring in the Combined Data for the Week, pull the instruments, and generate the plots back. 
```{r}
#| eval: FALSE
Instrument <- TheData |> dplyr::pull(Instrument) |> unique()

purrr::walk(.f=iLabPlots, .x=Instrument, data=TheData)
```

# Plotting Summary Plot

```{r}
#| eval: FALSE
iLabSummaryPlot(data=TheData)
```


```{r}
sessionInfo()
```
