---
title: "Setting up schedule monitor"
format: html
---

Begin by attaching `Bucephala` to your local environment via the `library()` call. 

```{r}
library(Bucephala)
```

If this is your first time getting setup, go ahead and create your associated storage folders. 

```{r}
#| eval: FALSE
FolderSetup()
```

Once this is done, proceed to set up a headless-browser session via chromote (make sure to have your phone handy for the 2FA)

```{r}
#| eval: FALSE
Active <- BrowserRun()
Active$view()
```

At this point you should be able to scrape the data. 

# Scraping the Data

This is where the main customization between sites occurs. Thus being kept intentionally external, with the data.frame then being passed to `Bucephala` from where it can operate. 

```{r}
Canto <- "282295#" #1
LSRII <- "282294#" #2
Aria <- "282292#" #3
Aurora3 <- "349299#" #4
Aurora4 <- "456489#" #5
Aurora5 <- "512453#" #6
AuroraCS <- "512475#" #7
MACSQuant10 <- "454785#" #8
Amnis <- "305467#" #9

Instrument <- c(Canto, LSRII, Aria, Aurora3, Aurora4, Aurora5, AuroraCS, MACSQuant10, Amnis)

Data <- data.frame(
  TheInstrument = c("Canto", "LSRII", "Aria", "Aurora3", "Aurora4", "Aurora5", "AuroraCS", "MACSQuant10", "Amnis"),
  Code = c(Canto, LSRII, Aria, Aurora3, Aurora4, Aurora5, AuroraCS, MACSQuant10, Amnis)
)
```

With the data.frame ready, we can map it in, returning the parsed schedules for individual instruments

```{r}
CompleteDataset <- purrr::map(.f=iLabScraper, .x=Instrument, chromote_session=Active,
    InstrumentSet=Data)
```

```{r}
TheData <- purrr::compact(CompleteDataset) |> dplyr::bind_rows()
#write.csv(CompleteDataset, "data/ActiveData.csv", row.names=FALSE)
#TheData <- read.csv("data/ActiveData.csv", check.names=FALSE)
```

```{r}
Instrument <- c("Canto", "LSRII", "Aria", "Aurora3", "Aurora4", "Aurora5", "AuroraCS", "MACSQuant10", "Amnis")

purrr::walk(.f=iLabPlots, .x=Instrument, data=TheData)
```

```{r}
Instrument <- c("Canto", "LSRII", "Aria", "Aurora3", "Aurora4", "Aurora5", "AuroraCS", "MACSQuant10", "Amnis") 
data <- TheData
```
